Model Recognition as Planning

### 2018-11-17 doc/icaps-19/model-recognition.tex
Updated navigation policies results

Figure \ref{fig:navigation_acc} shows the classification {\em accuracy} achieved by {\em model recognition as planning} with respect to a range of different degrees of observability, from 0\% to 100\% with 10\% increments. In this experiment we included the 0\% case which corresponds to observations where only the initial and final states are observed. The figure shows that for 0\% observability we were unable to unmistakably identify the generating navigation policies, but starting from 10\% we start to correctly classify most of the observations. Accuracy stabilizes in the range 0.875 to 1 which means that, at most, only 1 observation of the 8 was not correctly classified.

>>>>

Figure \ref{fig:navigation_acc} shows the classification {\em accuracy} achieved by {\em model recognition as planning} with respect to a range of degrees of observability, from 0\% to 100\% with 10\% increments. In this experiment we included the 0\% case which corresponds to observations where only the initial and final states are observed. The figure shows that for 0\% observability we were unable to unmistakably identify the generating navigation policies, but starting from 10\% we start to correctly classify half of the observations. Accuracy stabilizes after 40\% observability in the range 0.875 to 1 which means that, at most, only 1 observation of the 8 was not correctly classified.
